Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-21 prop_letter.tex
copy prop_letter.pptx to prop_short.pptm ...

\begin{definition}Given a Hilbert space of dimension\nb$d\ge3$, for every
  QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, any
  observable\nb$\mathbf{O}$ with spectral decomposition
  $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, and any minimal
  sub-event space $\events'$ containing
  $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
\end{equation}
\end{definition}

>>>>

\begin{definition}Given a Hilbert space of dimension\nb$d\ge3$, for every
  QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, any
  observable\nb$\mathbf{O}$ with spectral decomposition
  $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, and the minimal
  sub-event space $\events'$ containing
  $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
\end{equation}
\end{definition}
